Theoretical prediction of disrupted Min oscillation in flattened \emph{Escherichia coli}

### 2015-03-30 paper/plos.tex
updated correlation times in paper Tested everything on crystal.

%% \begin{figure}
%%   \begin{center}
%%     \includegraphics[height=6.4cm]{../data/shape-randst/0_40-18_50-18_50-95_00-15_00-full_array/plots/correlation.pdf}\\
%%     \includegraphics[height=6.4cm]{../data/shape-stad/0_40-2_35-1_32-0_00-15_00-full_array/plots/correlation.pdf}
%%   \end{center}
%%   \caption{Temporal correlation function of the total MinD found in
%%     two opposite polar regions of the shape \emph{A} (above) and the
%%     stadium \emph{A} (below) cell shapes, shown against the
%%     correlation time.  Data for both the the determinisitic and
%%     stochastic models are shown, and the correlation functions are
%%     scaled to have the same initial value.  For shape \emph{A}, the
%%     stochastic model shows an oscillation period of 52 seconds and
%%     coherence time of 248 seconds, so that it takes roughly 4.8
%%     periods for the behavior to decohere.  For the stadium \emph{A},
%%     the same model shows an oscillation period of 48.4 seconds and
%%     coherence time of 634 seconds, so that it takes roughly 13
%%     periods for the behavior to decohere.}
%%   \label{fig:corr-pancake-A}
%% \end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=8.7cm]{../data/shape-randst/0_40-18_60-28_60-94_00-15_00-full_array/plots/correlation.pdf}
    \includegraphics[width=8.7cm]{../data/shape-stad/0_40-2_92-1_18-0_00-15_00-full_array/plots/correlation.pdf}
  \end{center}
  \caption{Temporal correlation function of the total MinD found in
    two opposite polar regions of the shape \emph{B} (above) and the
    stadium \emph{B} (below) cell shapes, shown against the
    correlation time.  Data for both the the deterministic and
    stochastic models are shown, and the correlation functions are
    scaled to have the same initial value.  For shape \emph{B}, the
    stochastic model shows an oscillation period of 58 seconds and
    coherence time of 289 seconds, so that it takes roughly 5 periods
    for the behavior to decohere.  For the stadium \emph{B}, the same
    model shows an oscillation period of 51 seconds and coherence time
    of 442 seconds, so that it takes roughly 8.6 periods for the
    behavior to decohere.}
  \label{fig:corr-B}
\end{figure}

@@

We see that both in the shape \emph{B} and stadium \emph{B}, the
deterministic model is perfectly periodic.  Both the deterministic and
stochastic model correlations have the same number of proteins in
their cells, and have been normalized with the same normalization
factor, so that they can be directly compared against each other.  The
stochastic simulation of shape \emph{B} has a coherence time of 5
periods, while the corresponding simulation of stadium \emph{B} has a
coherence time of 8.6 periods.
%
The correlation function for stadium \emph{A} is similar to that of
stadium~\emph{B}, with similar coherence time (13 periods, not shown),
while shape~\emph{A} also exhibits a similar coherence time (4.9
periods).  This confirms that the stadium shapes do indeed oscillate
somewhat more regularly than the irregular shapes, but both are
comparable to the wild-type pill shape.
%
From the stochastic correlation data, we conclude that irregularity of
shape has only a moderate affect on the temporal regularity of the
oscillatory behavior, with even the very distorted shape~\emph{B}
exhibiting only a factor of two greater decoherence.

>>>>

%% \begin{figure}
%%   \begin{center}
%%     \includegraphics[height=6.4cm]{../data/shape-randst/0_40-18_50-18_50-95_00-15_00-full_array/plots/correlation.pdf}\\
%%     \includegraphics[height=6.4cm]{../data/shape-stad/0_40-2_35-1_32-0_00-15_00-full_array/plots/correlation.pdf}
%%   \end{center}
%%   \caption{Temporal correlation function of the total MinD found in
%%     two opposite polar regions of the shape \emph{A} (above) and the
%%     stadium \emph{A} (below) cell shapes, shown against the
%%     correlation time.  Data for both the the determinisitic and
%%     stochastic models are shown, and the correlation functions are
%%     scaled to have the same initial value.  For shape \emph{A}, the
%%     stochastic model shows an oscillation period of 52 seconds and
%%     coherence time of 288 seconds, so that it takes roughly 5.5
%%     periods for the behavior to decohere.  For the stadium \emph{A},
%%     the same model shows an oscillation period of 48.4 seconds and
%%     coherence time of 638 seconds, so that it takes roughly 13
%%     periods for the behavior to decohere.}
%%   \label{fig:corr-pancake-A}
%% \end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=8.7cm]{../data/shape-randst/0_40-18_60-28_60-94_00-15_00-full_array/plots/correlation.pdf}
    \includegraphics[width=8.7cm]{../data/shape-stad/0_40-2_92-1_18-0_00-15_00-full_array/plots/correlation.pdf}
  \end{center}
  \caption{Temporal correlation function of the total MinD found in
    two opposite polar regions of the shape \emph{B} (above) and the
    stadium \emph{B} (below) cell shapes, shown against the
    correlation time.  Data for both the the deterministic and
    stochastic models are shown, and the correlation functions are
    scaled to have the same initial value.  For shape \emph{B}, the
    stochastic model shows an oscillation period of 58 seconds and
    coherence time of 306 seconds, so that it takes roughly 5.3 periods
    for the behavior to decohere.  For the stadium \emph{B}, the same
    model shows an oscillation period of 51 seconds and coherence time
    of 442 seconds, so that it takes roughly 8.6 periods for the
    behavior to decohere.}
  \label{fig:corr-B}
\end{figure}

@@

We see that both in the shape \emph{B} and stadium \emph{B}, the
deterministic model is perfectly periodic.  Both the deterministic and
stochastic model correlations have the same number of proteins in
their cells, and have been normalized with the same normalization
factor, so that they can be directly compared against each other.  The
stochastic simulation of shape \emph{B} has a coherence time of 5.3
periods, while the corresponding simulation of stadium \emph{B} has a
coherence time of 8.6 periods.
%
The correlation function for stadium \emph{A} is similar to that of
stadium~\emph{B}, with similar coherence time (13 periods, not shown),
while shape~\emph{A} also exhibits a similar coherence time (5.5
periods).  This confirms that the stadium shapes do indeed oscillate
somewhat more regularly than the irregular shapes, but both are
comparable to the wild-type pill shape.
%
From the stochastic correlation data, we conclude that irregularity of
shape has only a moderate affect on the temporal regularity of the
oscillatory behavior, with even the very distorted shape~\emph{B}
exhibiting only a factor of two greater decoherence.
